---
title: "Lab 1 example problems"
output: github_document
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What percentage of parks in Vancouver have a public washroom?

### Part 1

Read the [City of Vancouver Parks washrooms data
set](https://opendata.vancouver.ca/explore/dataset/parks-washrooms/export/)
into R and calculate the number of unique parks in Vancouver that have a
washroom.

> Hint: use the `dplr` package `distinct` function to get the distinct
> number of rows for each parkID

```{r}
library(tidyverse)
```

```{r}
vancouver_park_washrooms <- read_delim("https://opendata.vancouver.ca/api/explore/v2.1/catalog/datasets/parks-washrooms/exports/csv?lang=en&timezone=America%2FLos_Angeles&use_labels=true&delimiter=%3B",
          delim = ";")
glimpse(vancouver_park_washrooms)
```

```{r}
num_park_washrooms <- distinct(vancouver_park_washrooms, ParkID) |> nrow()
num_park_washrooms
```

### Part 2

Use the [City of Vancouver Parks data
set](https://opendata.vancouver.ca/explore/dataset/parks/export/) to
calculate the percentage of parks in Vancouver that have a washroom.

```{r}
url <- "https://opendata.vancouver.ca/api/explore/v2.1/catalog/datasets/parks/exports/csv?lang=en&timezone=America%2FLos_Angeles&use_labels=true&delimiter=%3B"
vancouver_parks <- read_delim(url, delim = ";")
glimpse(vancouver_parks)
```

```{r}
num_vancouver_parks <- distinct(vancouver_parks, ParkID) |> nrow()
num_vancouver_parks
```

```{r}
num_park_washrooms / num_vancouver_parks * 100
```

## Tidying patient data

Consider the case where you have a patient data set and you are trying
to predict whether a patient has a iron deficiency using the
measurements from assays on their ferritin and hemoglobin levels. Is the
data below tidy? If not, tidy it so that it is.

```{r}
library(dplyr)
patients <- tibble(assay= c("ferritin", "hemoglobin", "iron deficiency"), 
       E2348 = c(14, 122, 0),
       E2349 = c(8, 103, 1),
       E2350 = c(31, 144, 0),
       E2351 = c(44, 98, 0),
       E2352 = c(27, 125, 0),
       E2353 = c(12, 131, 0))

patients
```

```{r}
patients_almost_tidy <- pivot_longer(patients,
             E2348:E2353,
             names_to = "patients",
             values_to = "results")
patients_almost_tidy
```

```{r}
patients_tidy <- pivot_wider(patients_almost_tidy,
            names_from = assay,
            values_from = results)
patients_tidy
```
