---
title: "Lab 1 example problems"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What percentage of parks in Vancouver have a public washroom?

### Part 1

Read the 
[City of Vancouver Parks washrooms data set](https://opendata.vancouver.ca/explore/dataset/parks-washrooms/export/) 
into R and calculate the number of unique parks in Vancouver that have a washroom.

> Hint: use the `dplr` package `distinct` function 
to get the distinct number of rows for each parkID

```{r}

```

### Part 2

Use the [City of Vancouver Parks data set](https://opendata.vancouver.ca/explore/dataset/parks/export/) to calculate the percentage of parks in Vancouver that have a washroom.

```{r}

```

## Tidying patient data

Consider the case where you have a patient data set 
and you are trying to predict whether a patient has a iron deficiency 
using the measurements from assays on their ferritin and hemoglobin levels.
Is the data below tidy? If not, tidy it so that it is.

```{r}
library(dplyr)
patients <- tibble(assay= c("ferritin", "hemoglobin", "iron deficiency"), 
       E2348 = c(14, 122, 0),
       E2349 = c(8, 103, 1),
       E2350 = c(31, 144, 0),
       E2351 = c(44, 98, 0),
       E2352 = c(27, 125, 0),
       E2353 = c(12, 131, 0))

patients
```

```{r}

```

```{r}

```