---
title: "Lecture 4 example problems"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Let's continue to play with some data 
# on the public art that exists in Vancouver!

Loading the data and reminding ourselves of what it looks like:

```{r}
art_data <- read_delim("https://opendata.vancouver.ca/api/explore/v2.1/catalog/datasets/public-art/exports/csv?lang=en&timezone=America%2FLos_Angeles&use_labels=true&delimiter=%3B",
                       delim = ";")
art_data
```

## Let's find the work of some artists we are interested in

Say we are interested in visiting public art of three well known 
indigenous artists in Vancouver:

- [Bill Reid](https://en.wikipedia.org/wiki/Bill_Reid)
- [Beau Dick](https://en.wikipedia.org/wiki/Beau_Dick)
- [Susan Point](https://en.wikipedia.org/wiki/Susan_Point)

Can we find the records that correspond the these from the `Artists` column?

```{r}

```

Wait? Nothing? 
I had read that some of their art was on public display in Vancouver...
Let's revisit the `Artists` column to see what is going on!

```{r}

```
Ohhhhhh - those don't look like artist names! 
Let's head back to the data dictionary:
<https://opendata.vancouver.ca/explore/dataset/public-art/information/>

## Getting the data we need!

The data we need to find the link between the artist names 
and the the artist identifier (ArtistID) is in the Public art - Artists data set:
<https://opendata.vancouver.ca/explore/dataset/public-art-artists/information/>

Let's read this data in 
and then use it to find the works of art by our artists of interest.

```{r}

```

The only columns we need from the `artist_data` dataframe are:

- `ArtistID`
- `FirstName`
- `LastName`

Lets drop the rest so that we aren't working with more data than we need:

```{r}

```

Now we can join `art_data` and `artist_data` 
to add the artist names to the `art_data` dataframe:

```{r}

```

We're almost ready to look up our artists! 
Last thing to do is to create a name column from the first and last names:

```{r}

```

Whoohoo! Let's find the art!

```{r}

```