---
title: "Lecture 4 example problems"
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Let's continue to play with some data

# on the public art that exists in Vancouver!

Loading the data and reminding ourselves of what it looks like:

```{r}
url <- "https://opendata.vancouver.ca/api/explore/v2.1/catalog/datasets/public-art/exports/csv?lang=en&timezone=America%2FLos_Angeles&use_labels=true&delimiter=%3B"
art_data <- read_delim(url,
                       delim = ";",
                       col_types = cols(Artists = col_character()))
art_data
```

## Let's find the work of some artists we are interested in

Say we are interested in visiting public art of five well known
indigenous artists in Vancouver:

-   [Bill Reid](https://en.wikipedia.org/wiki/Bill_Reid)
-   [Beau Dick](https://en.wikipedia.org/wiki/Beau_Dick)
-   [Charles Edenshaw](https://en.wikipedia.org/wiki/Charles_Edenshaw)
-   [Susan Point](https://en.wikipedia.org/wiki/Susan_Point)
-   [Sonny Assu](https://en.wikipedia.org/wiki/Sonny_Assu)

Can we find the records that correspond the these from the `Artists`
column?

```{r}
indigenous_artists <- c("Bill Reid",
                        "Beau Dick",
                        "Charles Edenshaw",
                        "Susan Point",
                        "Sonny Assu")

art_data |> 
  filter(Artists %in% indigenous_artists)
```

Wait? Nothing? I had read that some of their art was on public display
in Vancouver... Let's revisit the `Artists` column to see what is going
on!

```{r}
art_data |> select(Artists)
```

Ohhhhhh - those don't look like artist names! Let's head back to the
data dictionary:
<https://opendata.vancouver.ca/explore/dataset/public-art/information/>

## Getting the data we need!

The data we need to find the link between the artist names and the the
artist identifier (ArtistID) is in the Public art - Artists data set:
<https://opendata.vancouver.ca/explore/dataset/public-art-artists/information/>

Let's read this data in and then use it to find the works of art by our
artists of interest.

```{r}
url_artist <- "https://opendata.vancouver.ca/api/explore/v2.1/catalog/datasets/public-art-artists/exports/csv?lang=en&timezone=America%2FLos_Angeles&use_labels=true&delimiter=%3B"
artist_data <- read_delim(url_artist,
                          delim = ";")
artist_data
```

The only columns we need from the `artist_data` dataframe are:

-   `ArtistID`
-   `FirstName`
-   `LastName`

Lets drop the rest so that we aren't working with more data than we
need:

```{r}
artist_data <- artist_data |> 
  select(ArtistID, FirstName, LastName)
```

Now we would like to join `art_data` and `artist_data` to add the artist
names to the `art_data` dataframe, but remember that the `Artists`
column in `art_data` sometimes had multiple records in a row! We need to
separate those columns first and then tidy it!

Let's first find the maximum number of artists in an entry (so we know
how to separate it):

```{r}
artists <- art_data |> 
  pull(Artists) |> 
  str_split(",")

max_length <- 0
for (items in artists) {
  max_length <- max(length(items), max_length)
}
max_length
```

OK, let's separate into 17 columns! And then tidy!

```{r}
art_data_separated <- art_data |> 
  separate(Artists,
           into = paste0("Artist", 1:max_length),
           sep = ",",
           fill = "right",
           extra = "drop")
art_data_separated
```

```{r}
art_data_by_artist <- art_data_separated |> 
  pivot_longer(cols = starts_with("Artist"),
               names_to = NULL,
               values_to = "Artists") |> 
  mutate(Artists = as.numeric(Artists))
```

Now we can join `art_data_by_artist` and `artist_data` so we can find
the art created by our artists of interest!

```{r}
art_data_joined <- left_join(art_data_by_artist, artist_data,
          by = join_by(Artists == ArtistID))
```

We're almost ready to look up our artists! Last thing to do is to create
a name column from the first and last names:

```{r}
art_data_cleaned <- art_data_joined |> 
  unite("name",
        FirstName:LastName,
        sep = " ",
        na.rm = TRUE) 
```

Whoohoo! Let's find the art and write the data to a spreadsheet!

```{r}
art_data_cleaned |> 
  filter(name %in% indigenous_artists) |> 
  write_csv("indigenous-artwork.csv")
```
