---
title: "Lab 3 example problems"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Let's play with some data on the public art that exists in Vancouver!

```{r}
art_data <- read_delim("https://opendata.vancouver.ca/api/explore/v2.1/catalog/datasets/public-art/exports/csv?lang=en&timezone=America%2FLos_Angeles&use_labels=true&delimiter=%3B",
                       delim = ";")
art_data
```

## Let's do some data cleaning

Some work is untitled, but then has redundantly coded the type of work in the title column.
Let's try to remove these!

First we see how many of these we have!

```{r}
art_data |> ...(...(..., ...)
```

Now let's remove the redundant info:

```{r}
art_data <- art_data |> 
  ...(... = ...(..., ..., ...)) 
art_data |> 
  filter(str_detect(`Title of Work`, "Untitled \\("))
```

## What are the most common kinds of public art in Vancouver

How many different types of art are there in Vancouver?

```{r}
distinct(art_data, Type)
```

Let's now visualize the counts to help answer our question - what are the most common kinds of public art in Vancouver

```{r}
ggplot(art_data, aes(y = Type)) +
  geom_histogram(stat = "count")
```

Can we improve this figure? How? For example, what is the 4th most common kind of public art in Vancouver?
Yes, by using factors! Let's make the `Type` column a factor and order by frequency!
Since we are using the same column to order it, we will use `fct_infreq` 
from the `forcats` package (instead of `fct_reorder` where you can order based on a different column).

> Note - it also converts the column to a factor!
```{r}
art_data <- art_data |> 
  mutate(... = ...(...))
art_data
```

Let's remake our plot again:

```{r}
ggplot(art_data, aes(y = Type)) +
  geom_histogram(stat = "count")
```
